Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
merge

\ref{fig:unionfreq} shows the number of types inferred at each position of a
function signature. Most functions admit or return a uni-typed value. There are
\PercUnitypedPositions uni-typed parameter and return value positions in
function signatures. Only \PercManytypedPositions positions have more than three
types ascribed to them.

\input{tables/uni-typed-breakdown.tex}
\ref{fig:singlefreq} provides a breakdown of the different type categories
observed at uni-typed positions. Scalar, class and vector are
the most common type categories. The shaded rows correspond to polymorphic
types. Removing those gives us \CountMonomorphicPositions
(\PercMonomorphicPositions) monomorphic positions in a corpus of \CountPositions
parameter and return positions.

@@

\ref{fig:funpoly} shows the distribution of functions against the number of
polymorphic positions. We observe that \PercMonomorphicFunctions
(\CountMonomorphicFunctions) functions are monomorphic. The remaining
\PercPolymorphicFunctions (\CountPolymorphicFunctions) have at least one
polymorphic parameter or return type. Polymorphic functions are spread across
many packages, \CountMonomorphicPackages out of the 412 packages from our corpus
export only monomorphic functions.

>>>>

Figure~\ref{fig:unionfreq} shows the number of types inferred at each position of a
function signature. Most functions admit or return a uni-typed value. There are
\PercUnitypedPositions uni-typed parameter and return value positions in
function signatures. Only \PercManytypedPositions positions have more than three
types ascribed to them.

\input{tables/uni-typed-breakdown.tex}
Figure~\ref{fig:singlefreq} provides a breakdown of the different type categories
observed at uni-typed positions. Scalar, class and vector are
the most common type categories. The shaded rows correspond to polymorphic
types. Removing those gives us \CountMonomorphicPositions
(\PercMonomorphicPositions) monomorphic positions in a corpus of \CountPositions
parameter and return positions.

@@

Figure~\ref{fig:funpoly} shows the distribution of functions against the number of
polymorphic positions. We observe that \PercMonomorphicFunctions
(\CountMonomorphicFunctions) functions are monomorphic. The remaining
\PercPolymorphicFunctions (\CountPolymorphicFunctions) have at least one
polymorphic parameter or return type. Polymorphic functions are spread across
many packages, \CountMonomorphicPackages out of the 412 packages from our corpus
export only monomorphic functions.
